### 2015-10-08 untitled.tex
edited untitled.tex

One may consider to enrich the period enforcer with the following power: when the processor becomes idle, the task becomes ready to run right away regardless of the settings of eligibility time. Even with this, the above example remains valid by introducing a lowest priority task $\tau_3$ with execution time $C_3=13$ (to be executed from $3$ to $9$ and $13$ to $20$) and $T_3=D_3=100$.

>>>>

One may consider to enrich the period enforcer with the following power: when the processor becomes idle, the task becomes ready to run right away regardless of the settings of eligibility time. Even with this, the above example remains valid by introducing one additional lowest priority task $\tau_3$ with execution time $C_3=13$ (to be executed from $3$ to $9$ and $13$ to $20$) and $T_3=D_3=100$. With task $\tau_3$, the processor is always busy from time $0$ to time $23$.
